The Cost of Transportation : Spatial Analysis of US Fuel Prices

### 2017-09-04 Docs/Paper/paper.tex
slides

\cortext[cor1]{Corresponding author. Tel.: +0-000-000-0000 ; fax: +0-000-000-0000.}
\end{frontmatter}

@@

\bibliographystyle{elsarticle-harv}
\bibliography{biblio}
%

>>>>

\cortext[cor1]{Corresponding author. Tel.: +33140464000.}
\end{frontmatter}

@@

%\bibliographystyle{elsarticle-harv}
%\bibliography{biblio}
%

\begin{thebibliography}{16}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\href}[2]{#2}
\providecommand{\path}[1]{#1}
\providecommand{\DOIprefix}{doi:}
\providecommand{\ArXivprefix}{arXiv:}
\providecommand{\URLprefix}{URL: }
\providecommand{\Pubmedprefix}{pmid:}
\providecommand{\doi}[1]{\href{http://dx.doi.org/#1}{\path{#1}}}
\providecommand{\Pubmed}[1]{\href{pmid:#1}{\path{#1}}}
\providecommand{\bibinfo}[2]{#2}
\ifx\xfnm\relax \def\xfnm[#1]{\unskip,\space#1}\fi
%Type = Article
\bibitem[{Batty(2013)}]{batty2013big}
\bibinfo{author}{Batty, M.}, \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Big data, smart cities and city planning}.
\newblock \bibinfo{journal}{Dialogues in Human Geography} \bibinfo{volume}{3},
  \bibinfo{pages}{274--279}.
%Type = Article
\bibitem[{Brand et~al.(2013)Brand, Anable and Tran}]{brand2013accelerating}
\bibinfo{author}{Brand, C.}, \bibinfo{author}{Anable, J.},
  \bibinfo{author}{Tran, M.}, \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Accelerating the transformation to a low carbon
  passenger transport system: The role of car purchase taxes, feebates, road
  taxes and scrappage incentives in the uk}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{49}, \bibinfo{pages}{132--148}.
%Type = Article
\bibitem[{Brunsdon et~al.(1996)Brunsdon, Fotheringham and
  Charlton}]{brunsdon1996geographically}
\bibinfo{author}{Brunsdon, C.}, \bibinfo{author}{Fotheringham, A.S.},
  \bibinfo{author}{Charlton, M.E.}, \bibinfo{year}{1996}.
\newblock \bibinfo{title}{Geographically weighted regression: a method for
  exploring spatial nonstationarity}.
\newblock \bibinfo{journal}{Geographical analysis} \bibinfo{volume}{28},
  \bibinfo{pages}{281--298}.
%Type = Article
\bibitem[{Chen and Truong(2012)}]{chen2012using}
\bibinfo{author}{Chen, D.R.}, \bibinfo{author}{Truong, K.},
  \bibinfo{year}{2012}.
\newblock \bibinfo{title}{Using multilevel modeling and geographically weighted
  regression to identify spatial variations in the relationship between
  place-level disadvantages and obesity in taiwan}.
\newblock \bibinfo{journal}{Applied Geography} \bibinfo{volume}{32},
  \bibinfo{pages}{737--745}.
%Type = Article
\bibitem[{Combes and Lafourcade(2005)}]{combes2005transport}
\bibinfo{author}{Combes, P.P.}, \bibinfo{author}{Lafourcade, M.},
  \bibinfo{year}{2005}.
\newblock \bibinfo{title}{Transport costs: measures, determinants, and regional
  policy implications for france}.
\newblock \bibinfo{journal}{Journal of Economic Geography} \bibinfo{volume}{5},
  \bibinfo{pages}{319--349}.
%Type = Article
\bibitem[{Deltas(2008)}]{deltas2008retail}
\bibinfo{author}{Deltas, G.}, \bibinfo{year}{2008}.
\newblock \bibinfo{title}{Retail gasoline price dynamics and local market
  power}.
\newblock \bibinfo{journal}{The Journal of Industrial Economics}
  \bibinfo{volume}{56}, \bibinfo{pages}{613--628}.
%Type = Article
\bibitem[{Eckert(2013)}]{eckert2013empirical}
\bibinfo{author}{Eckert, A.}, \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Empirical studies of gasoline retailing: A guide to
  the literature}.
\newblock \bibinfo{journal}{Journal of Economic Surveys} \bibinfo{volume}{27},
  \bibinfo{pages}{140--166}.
%Type = Article
\bibitem[{Fullerton and West(2002)}]{fullerton2002can}
\bibinfo{author}{Fullerton, D.}, \bibinfo{author}{West, S.E.},
  \bibinfo{year}{2002}.
\newblock \bibinfo{title}{Can taxes on cars and on gasoline mimic an
  unavailable tax on emissions?}
\newblock \bibinfo{journal}{Journal of Environmental Economics and Management}
  \bibinfo{volume}{43}, \bibinfo{pages}{135--157}.
%Type = Article
\bibitem[{Gautier and Saout(2015)}]{gautier2015dynamics}
\bibinfo{author}{Gautier, E.}, \bibinfo{author}{Saout, R.L.},
  \bibinfo{year}{2015}.
\newblock \bibinfo{title}{The dynamics of gasoline prices: Evidence from daily
  french micro data}.
\newblock \bibinfo{journal}{Journal of Money, Credit and Banking}
  \bibinfo{volume}{47}, \bibinfo{pages}{1063--1089}.
%Type = Article
\bibitem[{Gregg et~al.(2009)Gregg, Losey, Andres, Blasing and
  Marland}]{gregg2009temporal}
\bibinfo{author}{Gregg, J.S.}, \bibinfo{author}{Losey, L.M.},
  \bibinfo{author}{Andres, R.J.}, \bibinfo{author}{Blasing, T.},
  \bibinfo{author}{Marland, G.}, \bibinfo{year}{2009}.
\newblock \bibinfo{title}{The temporal and spatial distribution of carbon
  dioxide emissions from fossil-fuel use in north america}.
\newblock \bibinfo{journal}{Journal of Applied Meteorology and Climatology}
  \bibinfo{volume}{48}, \bibinfo{pages}{2528--2542}.
%Type = Inproceedings
\bibitem[{Lee et~al.(2009)Lee, Kang and Kim}]{lee2009determinants}
\bibinfo{author}{Lee, S.}, \bibinfo{author}{Kang, D.}, \bibinfo{author}{Kim,
  M.}, \bibinfo{year}{2009}.
\newblock \bibinfo{title}{Determinants of crime incidence in korea: a mixed gwr
  approach}, in: \bibinfo{booktitle}{World conference of the spatial
  econometrics association}, pp. \bibinfo{pages}{8--10}.
%Type = Article
\bibitem[{Macharis et~al.(2010)Macharis, Van~Hoeck, Pekin and
  Van~Lier}]{macharis2010decision}
\bibinfo{author}{Macharis, C.}, \bibinfo{author}{Van~Hoeck, E.},
  \bibinfo{author}{Pekin, E.}, \bibinfo{author}{Van~Lier, T.},
  \bibinfo{year}{2010}.
\newblock \bibinfo{title}{A decision analysis framework for intermodal
  transport: Comparing fuel price increases and the internalisation of external
  costs}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{44}, \bibinfo{pages}{550--561}.
%Type = Article
\bibitem[{Rietveld et~al.(2001)Rietveld, Bruinsma and
  Van~Vuuren}]{rietveld2001spatial}
\bibinfo{author}{Rietveld, P.}, \bibinfo{author}{Bruinsma, F.},
  \bibinfo{author}{Van~Vuuren, D.}, \bibinfo{year}{2001}.
\newblock \bibinfo{title}{Spatial graduation of fuel taxes; consequences for
  cross-border and domestic fuelling}.
\newblock \bibinfo{journal}{Transportation Research Part A: Policy and
  Practice} \bibinfo{volume}{35}, \bibinfo{pages}{433--457}.
%Type = Article
\bibitem[{Rietveld and van Woudenberg(2005)}]{rietveld2005fuel}
\bibinfo{author}{Rietveld, P.}, \bibinfo{author}{van Woudenberg, S.},
  \bibinfo{year}{2005}.
\newblock \bibinfo{title}{Why fuel prices differ}.
\newblock \bibinfo{journal}{Energy Economics} \bibinfo{volume}{27},
  \bibinfo{pages}{79--92}.
%Type = Article
\bibitem[{Tan et~al.(2013)Tan, Blake, Saleh and Dustdar}]{tan2013social}
\bibinfo{author}{Tan, W.}, \bibinfo{author}{Blake, M.B.},
  \bibinfo{author}{Saleh, I.}, \bibinfo{author}{Dustdar, S.},
  \bibinfo{year}{2013}.
\newblock \bibinfo{title}{Social-network-sourced big data analytics}.
\newblock \bibinfo{journal}{IEEE Internet Computing} \bibinfo{volume}{17},
  \bibinfo{pages}{62--69}.
%Type = Article
\bibitem[{Tsai(2005)}]{tsai2005quantifying}
\bibinfo{author}{Tsai, Y.H.}, \bibinfo{year}{2005}.
\newblock \bibinfo{title}{Quantifying urban form: compactness versus' sprawl'}.
\newblock \bibinfo{journal}{Urban studies} \bibinfo{volume}{42},
  \bibinfo{pages}{141--161}.

\end{thebibliography}
